On exponential sums arising from the classical doubling method

### 2025-03-27 main.tex
lemmas cochar_computation and indep_geo_conj proofs case by case now
updated lemmas cochar_computation and indep_geo_conj to be case by case proofs.

For a torus character pair $(\algebraicGroup{T},\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset \algebraicGroup{G}^*$ and an embedding $\rho:\algebraicGroup{G}^* \to \algebraicGroup{\GL}_n$.  Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$ which contains $\rho(\algebraicGroup{T}^*)$. Let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
    \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
\]
The following lemma shows that this is well defined.

\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}[(i)]
	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
	\[
	g_{T,\rho}(\theta,\psi,\chi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
	\]
	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
	\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
	\]
	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
	\[
	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
	\]
	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{proof}

\begin{corollary}
\label{cor:geoconj}
Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
\end{corollary}
\begin{proof}
Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
\end{proof}

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below. 
\begin{center}
\begin{tabular}{ c c}
 Group & Dual group representations $\rho$ \\ 
 $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
 $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
 $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
 $GO(2n)$ & ? \\
 $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
 $GO(2n+1)$ & ? \\ 
  $U(n)$  & $U(n) \to \GL(2n)$  
\end{tabular}
\end{center}
Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$. In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$. In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.

In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.

@@

        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$

@@

@@

\calvin{can cut this next part but for the sake of completeness in early drafts lets keep it:}

@@

\calvin{end cut part}
Now the results follow from checking that
    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
for $r$ divisible as above.

@@

@@

Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$. We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$. We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$. \Cref{lem:cochar_computation} above implies that
\[
g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\calvin{check if we need a $\chi$ in the $\tau$ factor}
\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\

>>>>

For a torus character pair $(\algebraicGroup{T},\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset \algebraicGroup{G}^*$ and an embedding $\rho:\algebraicGroup{G}^* \to \algebraicGroup{\GL}_n$.  Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$ which contains $\rho(\algebraicGroup{T}^*)$. Let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$. Define
\[
    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \varepsilon_{\algebraicGroup{
    \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
\]
The following lemma shows that this is well defined.

\begin{lemma}
\label{lemma:gl_invariance}
\begin{enumerate}[(i)]
	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s)$.
	\item $g_{T,\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}[(i)]
	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
	\[
	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
	\]
	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
	\[
	g_{(s)}(\psi,\chi) := g_{T,\rho}(\chi,\theta,\psi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
	\]
	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
	\[
	g_{T,\rho}(\chi,\theta,\psi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
	\]
	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
\end{enumerate}
\end{proof}

\begin{corollary}
\label{cor:geoconj}
Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
\end{corollary}
\begin{proof}
Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
\end{proof}

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate $\rho$ in the table below. 
\begin{center}
\begin{tabular}{ c c}
 Group & Dual group representations $\rho$ \\ 
 $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
 $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
 $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
 $GO(2n)$ & ? \\
 $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
 $GO(2n+1)$ & ? \\ 
  $U(n)$  & $U(n) \to \GL(2n)$  
\end{tabular}
\end{center}
Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$. In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$. In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.

In particular to analyze $g_{T,\rho}(\chi,\theta,\psi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.

@@

        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases. Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w_nww_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$

@@

        0 & w_nwww_n

@@

@@

Now the results follow from the equalities
\begin{align*}
	\alpha(\zeta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\alpha(\zeta^{(y_1+qy_2 + \hdots +q^{n-1}y_{n})}) \alpha^{-1}(\zeta^{(y_{n+1}+qy_{n+2} + \hdots +q^{n-1}y_{2n})}) \\
	\theta(\beta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{n+2} \hdots +q^{2n-1}y_{2n})}) \\
	&=\theta'(\zeta^{(y_1+q(y_2) + \hdots +q^{2n-1}y_{2n})})\\
	\alpha(\zeta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots -q^{n-1}(y_{n}-y_{2n}))})&= \alpha(\zeta^{(y_1+qy_{n+2}+q^2y_3 +q^3y_4 \hdots +q^{n-1}y_{2n})}) \alpha^{-1}(\zeta^{(y_{n+1}+q(y_{2}) + q^2y_{n+3}\hdots +q^{n-1}y_{n})}) \\
	\theta(\beta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_{n+2} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{2n})}) \\
	&=\theta'(\zeta^{(y_1+qy_2 + \hdots +q^{2n-1}y_{2n})})
%Now the results follow from checking that
%\[
%    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
%\]
%for $r$ divisible as above.

@@

We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 
Let $\phi_{U,\lambda_i}$ denote the $\phi$'s above in cases 3 and 4 with $n = |\lambda_i|$.

@@

For the former we will show
\[
g_{T,\rho}(\chi,\theta,\psi)= g_{T}(\chi,\theta,\psi) \cdot \begin{cases}
        1  & G \neq Sp, GSp\\
        \tau{\chi}{\psi} & G = Sp \textnormal{ or } GSp
    \end{cases}.
\]
\calvin{$\chi$ or $\chi^{-1}$? Check throughout proof!}
We will do this casewise, demonstrating in each case that the Frobeinus equivariant map $X_*(\algebraicGroup{T}) \to X_*(\algebraicGroup{G})$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}. Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.

\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}}.
    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
	and applying \Cref{lem:cochar_computation}
	\begin{align*}
		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i} \begin{cases}
			\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
			\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
		\end{cases}
	which is equal to $g_{T}(\chi,\theta,\psi)$.
	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} $$
	and applying \Cref{lem:cochar_computation}
	\begin{align*}
		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \times \Pi_{\lambda_i^-}\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
	which is equal to $g_{T}(\chi,\theta,\psi)$.
	\item[($\algebraicGroup{Sp}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} \oplus \left(0:X_*(\algebraicGroup{T}) \to \mathbb{Z}\right)$$
	applying \Cref{lem:cochar_computation}
	\begin{align*}
		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
		\times \tau{\chi}{\psi}
	which is equal to $g_{T}(\chi,\theta,\psi) \cdot \tau(\chi,\psi)$.
	\item[($\algebraicGroup{SO}_{2n}^+$)] Let $T$ correspond to the signed permutation conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
	applying \Cref{lem:cochar_computation}
	\begin{align*}
		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
	which is equal to $g_{T}(\chi,\theta,\psi)$.
	\item[($\algebraicGroup{SO}_{2n}^-$)] Let $T$ correspond to the $(-n,n)$-twisted permutation conjugacy class $[w]$ with cycle decompositionof $[w \cdot (-n,n)]$ equal to $(\lambda^+,\lambda^-)$ 
	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
	applying \Cref{lem:cochar_computation}
	\begin{align*}
		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
	which is equal to $g_{T}(\chi,\theta,\psi)$.

\begin{comment}
We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
